### 2015-02-02 paper/model.tex
saving x_true,x_est,f with output; adding paper template

\documentclass[twocolumn,10pt]{article}
\usepackage{amsmath}

\begin{document}

@@

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
  P_{hyst_{v-t}} = \begin{cases}
    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
    0 & \mathrm{otherwise.}
  \end{cases}
\end{equation}
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers: \begin{equation}
  P_{load_t} = -\xi \cdot N_{t},
\end{equation}
where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.

@@

\end{document}

>>>>

%!TEX root = main.tex

@@

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
  P_{hyst_{v-t}} = \begin{dcases}
    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
    0 & \mathrm{otherwise.}
  \end{dcases}
\end{equation}
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers: \begin{equation}
  P_{load_t} = -\xi \cdot N_{t},
\end{equation}
where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.

@@
